Exoplanet population inference and the abundance \\ of Earth analogs from noisy, incomplete catalogs

### 2014-08-28 document/ms.tex
comments from morton

Implicit in the expression for the transit probability in \eq{transitprob} is
the assumption that all of the planets are on circular orbits.
Recently, \citet{kipping} demonstrated that when eccentric orbits are
included, our given value is an underestimate by about 10\%.
This effect will propagate directly to our inferred rate densities.
Even though the degeneracy is not exact---due to our choice of priors on the
rate density parameters---it is not a bad approximation to assume that it is
and scale the results down by your preferred factor.
The right thing to do would be to marginalize over this effect directly during
inference but that exercise is beyond the scope of the current \paper.

@@

Under the assumptions that we have made here, our inference of the occurrence
rate density of exoplanets places a probabilistic constraint on the number of
transiting Earth analogs in the existing \kepler\ dataset.
If we adopt the definition of ``Earth-like'' from \citet[][$200 \le
\period/\mathrm{day} < 400$ and $1 \le \radius/\radius_\oplus < 2$]{petigura},
and integrate the product inferred rate density function and the geometric
transit probability (\eqalt{transitprob}) over this bin, we find that the
expected number of Earth-like exoplanets transiting the stars in the sample of
Sun-like stars chosen by \citet{petigura} is
\begin{eqnarray}\eqlabel{ntransit}
N_{\oplus,\,\mathrm{transiting}} &=& 10.6_{-4.5}^{+5.9}
\end{eqnarray}
where the uncertainties are only on the expectation value and don't include
the Poisson sampling variance.
This is an exciting result because it means that, if we can improve the
sensitivity of exoplanet search pipelines to small planets orbiting on long
periods, then we should find some Earth analogs in the existing data.
Furthermore, because of the treatment of multiple transiting systems in the
catalog, the \True\ expected number of transiting Earth-like exoplanets
orbiting Sun-like stars is probably larger than the values in \eq{ntransit}!

>>>>

Implicit in the expression for the transit probability in \eq{transitprob} is
the assumption that all of the planets are on circular orbits.
Recently, \citet{kipping} demonstrated that when eccentric orbits are
included, our given value is an underestimate by about 10\%.
This effect will propagate directly to our inferred rate densities.
Even though the degeneracy is not exact---due to our choice of priors on the
rate density parameters---it is not a bad approximation to assume that it is
and scale the results down by your preferred factor.
The right thing to do would be to marginalize over this effect directly during
inference but that exercise is beyond the scope of the current \paper.
To complicate matters, the detection probability of a transit is also a
non-trivial function of the duration.
To account for this effect, so non-circular orbits should also be injected
when measuring the survey completeness.

@@

Under the assumptions that we have made here, our inference of the occurrence
rate density of exoplanets places a probabilistic constraint on the number of
transiting Earth analogs in the existing \kepler\ dataset.
If we adopt the definition of ``Earth-like'' from \citet[][$200 \le
\period/\mathrm{day} < 400$ and $1 \le \radius/\radius_\oplus < 2$]{petigura},
and integrate the product inferred rate density function and the geometric
transit probability (\eqalt{transitprob}) over this bin, we find that the
expected number of Earth-like exoplanets transiting the stars in the sample of
Sun-like stars chosen by \citet{petigura} is
\begin{eqnarray}\eqlabel{ntransit}
N_{\oplus,\,\mathrm{transiting}} &=& 10.6_{-4.5}^{+5.9}
\end{eqnarray}
where the uncertainties are only on the expectation value and don't include
the Poisson sampling variance.
This is an exciting result because it means that, if we can improve the
sensitivity of exoplanet search pipelines to small planets orbiting on long
periods, then we should find some Earth analogs in the existing data.
Furthermore, because of the treatment of multiple transiting systems in the
catalog, the \True\ expected number of transiting Earth-like exoplanets
orbiting Sun-like stars is almost certainly larger than the values in
\eq{ntransit}!
